---
title: "ML for Melanoma and Renal Cancer - Description of Data"
author: "Cameron Preasmyer"
date: "2025-08-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\begin{center}
\textbf{\Large Variables}
\end{center}


## Patient-Level Variables

- **Code**: Unique Patient ID Number  
- **Sex**: Sex of the Patient  
- **Metastasis**: Binary indicator of metastasis  
- **Images**: Binary indicator for patients with any images  
- **ANX_Image**: Binary indicator if patient has ANX specific image  
- **BCL2_Image**: Binary indicator if patient has BCL2 specific image  
- **BCL3_Image**: Binary indicator if patient has BCL3 specific image  
- **HX_Image**: Binary indicator if patient has HX specific image  
- **MITF_Image**: Binary indicator if patient has MITF specific image  
- **PBP_Image**: Binary indicator if patient has PBP specific image  
- **BRAF_Image**: Binary indicator if patient has BRAF specific image  
- **PIR_Image**: Binary indicator if patient has PIR specific image  
- **Metastasis_Date**: Date metastasis was confirmed  
- **Metastasis_Loc**: Location of metastasis  

## Histopathology

- **Hist_AJCC**: AJCC staging (initial)  
- **Hist_AJCC_Final**: AJCC staging (final)  
- **Hist_Breslow_mm**: Breslow depth in millimeters  
- **Hist_Ulceration**: Presence of ulceration  
- **Hist_Mitosis**: Mitosis count per mm²  

## Cytokine & Marker Expression

- **GM.CSF**: Granulocyte-macrophage colony-stimulating factor  
- **IL.4**: Interleukin-4 level  
- **IL.6**: Interleukin-6 level  
- **IL.10**: Interleukin-10 level  
- **IL.17A**: Interleukin-17A level  
- **IFN.y**: Interferon gamma level  
- **TGF.b**: Transforming growth factor beta level  
- **Dermcidina**: Dermcidin expression level  

## Immunohistochemistry & Gene Expression

- **IHC.BRAF**: Immunohistochemical result for BRAF  
- **PIRIN**: PIRIN expression level  
- **BCL2**: BCL2 expression level  
- **Linfos_BCL2.**: BCL2 expression in lymphocytes  
- **BCL3**: BCL3 expression level  
- **Linfos_BCL3.**: BCL3 expression in lymphocytes  
- **PEBP1**: PEBP1 expression level  
- **MITF**: MITF expression level  
- **ANX5**: ANX5 expression level  

## Tumor Microenvironment

- **infiltrado.linfoide**: Degree of lymphoid infiltration  
- **infiltrado.macrofagos**: Degree of macrophage infiltration  

\newpage

\begin{center}
\textbf{\Large Image Counts and Information}
\end{center}

\begin{center}
\textbf{The bar chart below shows and compares the counts of all image types in the data for metastatic/non-metastatic patients}
\end{center}
\space

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)

df <- read.csv('/Users/cameronpreasmyer/Desktop/Research\ Documents\ -\ ML\ for\ Melanoma/Cleaned\ CSV\ files/image_binaries.csv')
df <- df %>%
  mutate(Metastasis = if_else(is.na(Metastasis), 0, Metastasis))

image_vars <- c("Images", "ANX_image", "BCL2_image", "BCL3_image", "HX_image",
                "MITF_image", "PBP_image", "BRAF_image", "PIR_image")
df_long <- df %>%
  select(Code, Metastasis, all_of(image_vars)) %>%
  pivot_longer(cols = all_of(image_vars), names_to = "Image_Type", values_to = "Has_Image") %>%
  filter(Has_Image == 1)

image_summary <- df_long %>%
  group_by(Image_Type) %>%
  summarise(
    Total = n(),
    Metastasis_1 = sum(Metastasis == 1)
  ) %>%
  pivot_longer(cols = c(Total, Metastasis_1), names_to = "Group", values_to = "Count")

ggplot(image_summary, aes(x = reorder(Image_Type, -Count), y = Count, fill = Group)) +
  geom_bar(stat = "identity", position = "dodge", color = "black", width = 0.6) +
  scale_fill_manual(values = c("Total" = "#3182bd", "Metastasis_1" = "#e6550d"),
                    labels = c("Confirmed Metastasis", "Total Image Count")) +
  labs(title = "Image Type Counts - Total Count vs. Metastatic Patients",
       x = "Image Type",
       y = "Number of Patients",
       fill = "Group") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(face = "bold", size = 12, hjust = 0.5))
```

\begin{center}
\textbf{The pie charts below comapre the proportion of patients who have at least one image between metastitic patients and all patients}
\end{center}
  
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(patchwork)

meta_image_data <- df %>%
  filter(Metastasis == 1) %>%
  count(Has_Image = Images) %>%
  mutate(Group = if_else(Has_Image == 1, "Has 1+ Images", "No Images"))
all_image_data <- df %>%
  count(Has_Image = Images) %>%
  mutate(Group = if_else(Has_Image == 1, "Has 1+ Images", "No Images"))
meta_image_data <- meta_image_data %>%
  mutate(Prop = n / sum(n),
         Label = paste0(round(Prop * 100), "%"))
all_image_data <- all_image_data %>%
  mutate(Prop = n / sum(n),
         Label = paste0(round(Prop * 100), "%"))


p1 <- ggplot(meta_image_data, aes(x = "", y = n, fill = Group)) +
  geom_bar(stat = "identity", width = 1, color='grey15') +
  coord_polar("y") +
  geom_text(aes(label = Label), position = position_stack(vjust = 0.5), color = "black", size = 5) +
  labs(title = "Metastatic Patients") +
  theme_void() +
  theme(plot.title = element_text(face = "bold", size = 12,hjust=0.5))+
  scale_fill_manual(values = c("Has 1+ Images" = "lightblue2", "No Images" = "grey"))

p2 <- ggplot(all_image_data, aes(x = "", y = n, fill = Group)) +
  geom_bar(stat = "identity", width = 1, color='grey15') +
  coord_polar("y") +
  geom_text(aes(label = Label), position = position_stack(vjust = 0.5), color = "black", size = 5) +
  labs(title = "All Patients") +
  theme_void() +
  theme(plot.title = element_text(face = "bold", size = 12,hjust=0.5))+
  scale_fill_manual(values = c("Has 1+ Images" = "lightblue2", "No Images" = "grey"))
p1+p2

```


